Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-03-31 papers/intro_paper/intro_paper.tex
added responses to referee comments in section III B

To demonstrate the robustness of the method in detecting possible
deviations from GR, we inject synthetic GW signals which are identical to
the corresponding GR prediction up to merger, and differ in their post-merger
description. We again choose binary-parameters
similar to GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but
set $\df{220} = \dtau{220} = 0.1 $.
In other words, we assume that the frequency and damping time
of our non-GR signal is 10\% more than the corresponding GR prediction,
although the pre-merger signal is identical to GR. In Fig.~\ref{fig:nongr_waveform}
we show this non-GR waveform, \texttt{pSEOBNR} with respect to the 
original GR template, \texttt{SEOBNR}. We see that the waveforms are identical in amplitude
and instanteneous frequency upto the merger (lower panel) , beyond which the 
red (GR template) and blue (non-GR template) differ. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding
values of the injection parameters, indicated by the black dashed lines.

>>>>

To demonstrate the robustness of the method in detecting possible
deviations from GR, we inject synthetic GW signals which are identical to
the corresponding GR prediction up to merger, and differ in their post-merger
description. We again choose binary-parameters
similar to GW150914 and GW190521 (see Table ~\ref{tab:injection_values}), but
set $\df{220} = \dtau{220} = 0.1 $.
In other words, we assume that the frequency and damping time
of our non-GR signal is 10\% more than the corresponding GR prediction,
although the pre-merger signal is identical to GR. In Fig.~\ref{fig:nongr_waveform}
we show this non-GR waveform, \texttt{pSEOBNR} with respect to the 
original GR template, \texttt{SEOBNR}. We see that the waveforms are identical in amplitude
and instanteneous frequency upto the merger (lower panel) , beyond which the 
red (GR template) and blue (non-GR template) differ. We summarize the results of the Bayesian analysis in Fig.~\ref{fig:simulated_signal_nonGR} where we
show the posterior probability distributions for $(\df{220}, \dtau{220})$, or equivalently
$(\fngr{220}, \taungr{220})$. We find that they are consistent with the corresponding
values of the injection parameters, indicated by the black dashed lines. 
\abhi{We also note that at the SNRs we consider, since statistical uncertainties dominate systematic biases, the measurement excludes, at the 90\% credible level, the GR prediction on the frequency ($\df{220}=0$), but includes the prediction on the damping time ($\dtau{220}=0$). However, with louder events, one would expect these measurement errors to shrink and the $\taungr{220}$ measurement to be inconsistent with the GR prediction as well.}
